Democracy, Public Support, and Measurement Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
corrected the saving files
uncertain for apsr analyses

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

@@

>>>>

saveRDS(result_clsFullUncertainAPSR, file = here::here("output", "estimates_clsFullUncertainAPSR.RDS"))

@@

saveRDS(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoUncertainAPSR.RDS"))
```

```{r visualizedFullUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")
